Parsing Postfix log files

### 2008-07-28 doc/logparser-implementation.tex
Wrote minimum ruleset versus maximum ruleset section - largely taken from the SGAI paper.

XXX DUNNO IF THIS SECTION SHOULD BE HERE\@.  QUEUEID VS PID ISN'T TOO
IMPORTANT\@; CONNECTION REUSE COULD EASILY BE MOVED TO ADDITIONAL
COMPLICATIONS\@; RE-INJECTED MAILS SHOULD PROBABLY BE MOVED TO ADDITIONAL
COMPLICATIONS TOO\@.

@@

XXX CONSIDER REMOVING PART TWO OF THE FLOW CHART\@: I DON'T THINK THAT
RE-INJECTION IS IMPORTANT ENOUGH TO WARRANT IT\@.  THE EXPLANATION OF
TRACKING (\textsection{}5.4.3) COULD BE MOVED TO ADDITIONAL
COMPLICATIONS\@.

>>>>

XXX DUNNO IF THIS SECTION SHOULD BE HERE\@.  QUEUEID VS PID IS NOT TOO
IMPORTANT\@; CONNECTION REUSE COULD EASILY BE MOVED TO ADDITIONAL
COMPLICATIONS\@; RE-INJECTED MAILS SHOULD PROBABLY BE MOVED TO ADDITIONAL
COMPLICATIONS TOO\@.

@@

XXX CONSIDER REMOVING PART TWO OF THE FLOW CHART\@: I DO NOT THINK THAT
RE-INJECTION IS IMPORTANT ENOUGH TO WARRANT IT\@.  THE EXPLANATION OF
TRACKING (\textsection{}5.4.3) COULD BE MOVED TO ADDITIONAL
COMPLICATIONS\@.

### 2008-07-28 doc/logparser-other-parsers-review.tex
Wrote minimum ruleset versus maximum ruleset section - largely taken from the SGAI paper.

Logrep does not come with any documentation, though some scant
documentation is available on its website (\parsername{} provides copious
documentation).  It requires a web browser to interact with it, ensuring
that automated log processing will be difficult, whereas automated
processing is a key part of \parsernames{} design.  Sadly all the author's
attempts to use Logrep failed, as it was unable to access the log files
selected; this appears to be a bug rather than operator error.\footnote{If
it is caused by operator error, the interface needs improvement as the
(minimal) instructions were followed as closely as possible, and multiple
attempts were made.}  As parsing failed it wasn't possible to review the
reports Logrep can generate (available in \HTML{} only), nor to examine the
(undocumented) format in which it can save extracted data for subsequent
reuse.

>>>>

Logrep does not come with any documentation, though some scant
documentation is available on its website (\parsername{} provides copious
documentation).  It requires a web browser to interact with it, ensuring
that automated log processing will be difficult, whereas automated
processing is a key part of \parsernames{} design.  Sadly all the author's
attempts to use Logrep failed, as it was unable to access the log files
selected; this appears to be a bug rather than operator error.\footnote{If
it is caused by operator error, the interface needs improvement as the
(minimal) instructions were followed as closely as possible, and multiple
attempts were made.}  As parsing failed it was not possible to review the
reports Logrep can generate (available in \HTML{} only), nor to examine the
(undocumented) format in which it can save extracted data for subsequent
reuse.

### 2008-07-28 doc/logparser-results.tex
Renamed normal-vs-smaller graph to full-ruleset-vs-minimum-ruleset.
Wrote minimum ruleset versus maximum ruleset section - largely taken from the SGAI paper.

XXX DO SOMETHING WITH NORMAL VS SMALLER GRAPH\@.

@@

When generating the timing data used in this section, \numberOFlogFILES{}
log files (totaling 10.08 GB, \numberOFlogLINEShuman{} log lines) were each
parsed 10 times, the results from the first first run discarded, and the
execution time for the remaining 9 runs averaged.  The results from the
first run were discarded because because the rule ordering will be
sub-optimal compared to subsequent runs --- XXX MAYBE I SHOULDN'T DISCARD
THE FIRST RESULT\@?  Saving results to the database was disabled for the
test runs, as that dominates the run time of the program, and the tests are
aimed at measuring the speed of the parser rather than the speed of the
database and the disks the database is stored on.

@@

XXX WRITE THIS SECTION\@.

\showgraph{build/plot-normal-vs-smaller}{NORMAL VS SMALLER}{NORMAL VS
SMALLER}

>>>>

@@

When generating the timing data used in this section, \numberOFlogFILES{}
log files (totaling 10.08 GB, \numberOFlogLINEShuman{} log lines) were each
parsed 10 times, the results from the first first run discarded, and the
execution time for the remaining 9 runs averaged.  The results from the
first run were discarded because because the rule ordering will be
sub-optimal compared to subsequent runs --- XXX MAYBE I SHOULD NOT DISCARD
THE FIRST RESULT\@?  Saving results to the database was disabled for the
test runs, as that dominates the run time of the program, and the tests are
aimed at measuring the speed of the parser rather than the speed of the
database and the disks the database is stored on.

@@

How any architecture scales as the number of rules increases is important,
but it is particularly important in this architecture because it is
expected that the typical parser will have a large number of rules.  There
are \numberOFrules{} rules in the full Postfix ruleset, whereas the minimum
number of rules required to parse the \numberOFlogFILES{} log files used
when generating the results in this document is \numberOFrulesMINIMUM{},
\numberOFrulesMINIMUMpercentage{} of the full ruleset.  The full ruleset is
larger because the Postfix parser is tested with \numberOFlogFILESall{} log
files, to improve its parsing and ensure it correctly parses logs generated
by later Postfix versions.  A second set of statistics was generated using
the minimum ruleset and compared to the statistics generated using the full
ruleset: the percentage execution increase when using the full ruleset
instead of the minimal ruleset for normal, shuffled and reversed orderings
is shown in \graphref{Percentage parsing time increase of maximum ruleset
over minimum ruleset}.

\showgraph{build/plot-full-ruleset-vs-minimum-ruleset}{Percentage parsing
time increase of maximum ruleset over minimum ruleset}{Percentage parsing
time increase of maximum ruleset over minimum ruleset}

It is clear from \graphref{Percentage parsing time increase of maximum
ruleset over minimum ruleset} that the increased number of rules noticeably
increases parsing time with reverse ordering, and to a lesser extent with
shuffled ordering.  The normal ordering (where are the most frequently
matching rules are tried first) shows a mean increase of
\input{build/full-ruleset-vs-minimum-ruleset-include.tex} in parsing time
for a \numberOFrulesMAXIMUMpercentage{} increase in the number of rules.
Log files 22 and 62--68 show much smaller increases for shuffled and
reversed ordering than other log files do, because the majority of log
lines in those log files are parsed by Postfix components with a small
number of parsing rules, so removing unnecessary rules has little effect on
the total number of rules used.  These results show that the architecture
scales very well as the number of rules increases, and that optimally
sorting the rules is an important optimisation contributing to this
scalability.
